\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}


\section{Identification}
This user manual contains all the important information about setting up the
software and operating. When you purchase our software you will receive an email
which contains important information about the software and the client. It is
important that you save this information because it will allow us to identiy you
when you contact us. More information about how to reach us can be found in
section 1.8

\section{Copyright}

Virtual machine management system own the intellectual property rights. The
service contain content including  but not limited to the name of the software,
information, data and logo that are the property of VMMS and are protected by
U.S. and international copyright laws.

\section{Trademark notices}

VMMS, VMMS software, its slogan.. and its logo are all registered trademarks of
VMMS. All other trademarks and trade names mentioned in this document are the
property of their respective owners. 2017 VMMS All Rights Reserved.

\section{Restrictions}
The copyright material such as trademarks, interface design and software belong
exclusively to the owners.Making any changes, copies, modifications, reverse
engeering or decompiling it is prohibited without the explicit authorization of 
the respective owners.

\section{Warranties}
VMMS warrants only against software defects or failure for a period of one year
after its purchase. The replacement cost depends on the cause of the problem. A
full replacement is supported in case of severe damage in software or defect
which is of conceptual origin. If the software as purchased is modified by any
client, we declare the warranty to be void.

\section{Contractual obligations}

By using our software you agree with our terms of use. Therefore it is important
to carefully read our agreements before using our product. The agreements and
restrictions can be found above in section 1.4 and 1.5, you may also read
section 1.6. By using our software you agree to be bound by these Terms. If you
do not agree with our agreement then  please do not use our product. In case you
do not respect these terms we are forced to terminate or suspend access to our 
service immediately. In case such a case occurs you will receive an email with 
further details on how to proceed.



\section{Disclaimers}
The software is to be used at your own risk. VMMS is provided to you 'as is'.
This means with all faults and bugs that the software may contain. The software
that can be downloaded from our website will be virus-free however if you
download it, you do so at your own risk. You are responsible for any damage to
your computer system, this includes loss of data from the download or of any 
materials.\\\\In some jurisdictions, the law may not allow the disclaimer of
warranties, so some aspects of this section may not apply to you.


\section{Contact}
In case of questions, issues or bugs related with the software, the VMMS team
can be contacted either using the integrated message menu, via phone or
via post. Our hotline 802012 is open 7/7 from 8am to 4pm and our office is
located at 54 rue blabla).
